% !TEX program = XeLaTeX
\documentclass[11pt, a4paper]{article}

% \usepackage{fontspec}
% % Computer Modern from: https://cm-unicode.sourceforge.io/download.html
% \setmainfont{CMU Concrete}

% Margins
\usepackage[margin=2.75cm]{geometry}

% UK English
\usepackage[UKenglish]{babel}

% Bullet point spacing
\setlength{\itemsep}{0.1em}

% Remove page numbers
\pagenumbering{gobble}

% Reduce hyphenation
\pretolerance=5000
\tolerance=9000
\emergencystretch=10pt

% Line spacing
\usepackage{setspace}
\setstretch{1}

% URLs
\usepackage[hidelinks]{hyperref}

% Quotation marks
\usepackage{csquotes}

\begin{document}

% Header
\begin{center}
	{\huge Johannes Smit \\}
	\vspace{1em}
	{\large
	Email: \href{mailto:h@nnes.dev}{\nolinkurl{h@nnes.dev}} 
	\hfill
	Website: \href{https://ha.nnes.dev/}{\nolinkurl{ha.nnes.dev}}
	\hfill
	GitHub: \href{https://github.com/hasnep/}{\nolinkurl{github.com/hasnep}}
	\\
	}
\end{center}

% Personal statement
I am a Mathematics graduate with experience in both data science and software engineering.
Since joining Amey Strategic Consulting, I have been an analyst in a variety of projects and developed tools for internal process improvement.

\subsection*{Employment}

\begin{itemize}
	\item July 2019--Present: Strategic Consultant, Amey Strategic Consulting (London, UK)
	\begin{itemize}
		\item I am part of a team working with Amey Highways to deliver the \enquote{ADEPT Live Labs innovation programme} for Kent County Council, which aims to develop data-led approaches to managing the county's assets.
		This involved a building a PostgreSQL database and using Airflow to schedule data ingestion from many sources.
		To deliver a platform for data-driven decision making, I built a React dashboard using Plotly and Mapbox to clearly visualise the large amount of data.
		Other tasks included designing and building a proof of concept system to ingest and display realtime IoT data from multiple sensors and designing a machine learning timeseries model for workload prediction.
		
		\item I am a maintainer of the team's financial platform --- an R Shiny dashboard that allows team members and project managers to monitor expenditure, register risks, and keep track of invoices, while synchronising the data with a relational database.
		
		\item Using R, I collaborated with Amey's HR department to complete an analysis of the gender pay gap across all departments in wider Amey.
		The visualisations, statistics and forecasts were used to guide the company's decision making with regards to gender equality in pay rates.
		I then created a Python package to automatically perform these forecasts and trained an HR analyst with no prior Python knowledge to produce original analyses.
		
		\item I completed a focused two week analytics sprint on the maintenance contract fulfilled by Amey Highways for Staffordshire County Council.
		I collected user-stories and datasets from both the Amey and Staffordshire teams about the processes used and delivered a presentation of data visualisations, highlighting key successes and opportunities.
		
		\item I oversaw the deployment of a Python tool to automate sending email reminders for Amey TPT.
		This was a task that previously took multiple days each month but can now be performed in a few minutes, saving significant resource time.
	\end{itemize}

	\item June 2018--September 2018: Data Science Services Intern, Asia Analytics Taiwan (Taipei, Taiwan)
	\begin{itemize}
		\item In my internship, I used Python and R to write extensions for data cleansing and data mining in SPSS and SPSS Modeller.
		I quickly added features when they were requested, made an intuitive but powerful interface for the extensions and documented the process used.
		I also created an in-depth tutorial on programming using SPSS Syntax from scratch, demonstrating my ability to learn and clearly communicate concepts to an audience who were unfamiliar with the topic.
	\end{itemize}
\end{itemize}

\subsection*{Education}

\begin{itemize} 
	\item 2015--2019: MMath Mathematics --- 2:1 (University of Exeter, UK)

	My dissertation involved combining modern neural networks using Keras with more traditional regression and Gaussian processes models with the aim of providing more human-understandable insights to machine learning algorithms.
	I successfully modelled a neural network using multiple techniques in a way that simplified the complex internal system to well-understood statistical processes.
	Other modules included machine learning and spatio-temporal statistics.

	\item 2009--2015: Felpham Community College (Felpham, UK)

	My A-levels were Mathematics~(A), Further~Mathematics~(B), Physics~(B), AS~Spanish~(B) and STEP~Mathematics~(Level~3).
\end{itemize}

\subsection*{Certifications}

\begin{itemize}
\item Microsoft Certified: Azure Data Scientist Associate (September 2020)

\item Microsoft Certified: Azure Fundamentals (May 2020)
\end{itemize}

\subsection*{Skills}

\begin{itemize}
	\item As well as being fluent in Python and R for data analysis, I develop personal open-source projects in the languages Julia and Typescript as a hobby.
	For example, I created \texttt{DataSkimmer.jl}, a Julia package to quickly summarise tabular data in the terminal.
	All of my personal projects can be found on my website (\href{https://ha.nnes.dev/}{\nolinkurl{ha.nnes.dev}}).
	
	\item In school, I was a lead animator and team coordinator in the UK Schools Computer Animation Competition.
	Our team achieved first in our category twice, and received the \enquote{EA Recognition Award} in our third year.
	This experience improved my time management and strengthened my ability to lead a team in bringing a project to completion.
	
	\item Languages: English (native), Afrikaans (fluent), Spanish (intermediate) and Mandarin (beginner).
\end{itemize}

\noindent References are available on request.

\end{document}
